---
appendix: "appendix_2.Rmd"
---

# Example Data Analysis Code

## Libraries

```{r}
library(lavaan)
library(visualizemi)
library(rio)
# set the seed
set.seed(43843)
```

## Data

```{r eval = F}
# import the dataset here 
```

## Model Programming 

Program the model in `lavaan` syntax including all correlated errors or other adjustments noted by the original authors. 

```{r}
# example model 
HS.model <- ' visual  =~ x1 + x2 + x3
              textual =~ x4 + x5 + x6
              speed   =~ x7 + x8 + x9 '
```

## Use MGCFA function

Use the `mgcfa` function to run the proposed model steps. This model should replicate their model excluding any partial invariance steps. If they say they will run "residuals" but then do not because of partial invariance, only include up to the step that was invariant or partially invariant. 

```{r}
                    # cfa model
saved_mgcfa <- mgcfa(model = HS.model,
                     # dataset in data frame 
                     data = HolzingerSwineford1939, 
                     # grouping variable column as a character
                     group = "sex",
                     # lavaan syntax for group constraints
                     group.equal = c("loadings", "intercepts", "residuals"), 
                     # any other lavaan cfa arguments
                     meanstructure = TRUE)
```

## Review Model Outputs

Review model outputs to ensure they do not produce heywood cases or other errors. 

```{r}
# review the model outputs to ensure they do not produce errors
saved_mgcfa$model_fit

# overall
saved_mgcfa$model_overall

# groups
# saved_mgcfa$group_models$model.1
# saved_mgcfa$group_models$model.2

# configural
# saved_mgcfa$model_configural

# constraints
# saved_mgcfa$invariance_models$model.loadings
# saved_mgcfa$invariance_models$model.intercepts
# saved_mgcfa$invariance_models$model.residuals
```

## Replication Model Level 

Run the `bootstrap_model` function and determine the effect sizes for model level invariance steps. Use the same `group.equal` constraints as above. 

```{r}
saved_boot_model <- bootstrap_model(
  # saved configural model to start at
  saved_configural = saved_mgcfa$model_configural,
  # dataset for the analysis
  data = HolzingerSwineford1939,
  # model lavaan syntax
  model = HS.model,
  # group variable in the dataset
  group = "sex", 
  # number of bootstraps
  # this is set to a low number for testing
  nboot = 20,
  # name of the fit measure you want to use, make sure it's lavaan code
  invariance_index = "cfi",
  # rule for the difference in fit indices
  invariance_rule = .01,
  # what order of steps do you want to test? 
  group.equal = c("loadings", "intercepts", "residuals")
)

kable(saved_boot_model)
```

## Replication Parameter Level / Partial Invariance

If their model was invariant: use the last step as the `partial_step` option. If their model was partially invariant, use the step that was indicated as partially invariant (where they had to relax parameters - if they did this on more than one step, use the last one). 

```{r eval = F}
saved_boot_partial <- bootstrap_partial(
  # the model you want to test 
  # use the model before your invariant one
  # in this case it broke down at loadings
  saved_model = saved_mgcfa$model_configural,
  # the dataframe
  data = HolzingerSwineford1939,
  # the original model syntax
  model = HS.model,
  # the grouping variable column
  group = "sex",
  # run more but start low for testing
  nboot = 10,
  # what index are you using for invariance?
  # match this to lavaan's name under fitmeasures()
  invariance_index = "cfi",
  # what rule are you using?
  invariance_rule = .01,
  # what are we comparing against? 
  invariance_compare = unname(fitmeasures(saved_mgcfa$model_configural, "cfi")),
  # which step you want to estimate effect size for
  partial_step = c("loadings"), 
  # which parameters you want to hold constrained
  group.equal = c("loadings")
  )

kable(head(saved_boot_partial$boot_DF))

kable(saved_boot_partial$boot_summary)

kable(saved_boot_partial$boot_effects)

saved_boot_partial$invariance_plot

saved_boot_partial$effect_invariance_plot

saved_boot_partial$density_plot
```

