---
appendix: "appendix_1.Rmd"
---

# Appendix A

## Coding Survey

Note: this document was created in qualtrics and then downloaded into word format to upload into ChatGPT. We formatted it for ease of reading here. 

```{r}
library(knitr)
library(rio)
```

### Article Coding Form  

You will use this form to code articles for the Assessment of Assessment Project. You should fill out this form once for each article. If the article has multiple measurement invariance tests (i.e. once for sex and once for age), then you would fill out the article once for each test of measurement invariance within an article.
 
Note: the survey will end if your article does not have the required components we are looking for in the article. If you think you did something wrong, please ask or simply recode it.  

### doi_link

 Enter the article doi as an html link (i.e., https://doi.org/10.1177/107319119400100401) 

### invariance_yes 

Does this article report measurement invariance?
 
Search the document (control + F) for equal groups, invariance, multigroup. Notes:
 
- Code yes even if the data is simulated
- Code yes if item response theory differential item functioning is used - Code other for unsure or unclear or list your own reason  

  - Yes  (1) 
  -	No  (2) 
  - Other  (3) __________________________________________________

### cfa_irt 

Does this article use structural equation modeling (confirmatory factor analysis) or item response theory?  

- Structural Equation Modeling  (1) 
- Item Response Theory  (2) 
- Neither: List Analysis  (3) __________________________________________________

### real_data 

Does this article include real data (i.e., no simulation studies)?  

- Yes  (1) 
- No  (2) 
- Unclear  (3) __________________________________________________

### data 

Is the data accessible? Look for supplemental documents, links to files, and pages of correlation/covariance matrices.  

- Yes  (1) 
- Matrices included  (2) 
- Contact author  (3) 
- No  (4) 
- Unclear or broken links  (5) __________________________________________________

### scale_name 

What is the name of the instrument/scale they are testing? Please include the entire name, not the abbreviation.  

### scale_ref 

What is the citation of the scale they are testing? Copy from the reference section.

### group_number 

How many groups are compared?  

### group_names 

What sample groups are they comparing in this analysis? List groups the way they are described (i.e., do not correct Male/Female to Men/Women, use the names from the paper). Separate groups with a comma.  

### what_steps 

What steps of measurement invariance did they test? Please click all that were used. The names in parentheses are sometimes used to describe each step.  

- Equal form (configural)  (1) 
- Equal item loadings (metric)  (2) 
- Equal item intercepts/means (scalar)  (3) 
- Equal item thresholds  (4) 
- Equal item residuals (strict)  (5) 
- Equal item residual covariances  (8) 
- Equal latent means (population means)  (6) 
- Equal latent variances  (7) 
- Equal latent covariances  (9) 
- Equal regressions  (10) 

### step_order

Carry Forward Selected Choices from "What steps of measurement invariance did they test? Please click all that were used. The names in parentheses are sometimes used to describe each step. "
 
What order did they test the steps in? Please drag and drop them into the order found in the paper (often in a table).  

- Equal form (configural) (1)
- Equal item loadings (metric) (2)
- Equal item intercepts/means (scalar) (3)
- Equal item thresholds (4)
- Equal item residuals (strict) (5)
- Equal item residual covariances (6)
- Equal latent means (population means) (7)
- Equal latent variances (8)
- Equal latent covariances (9)
- Equal regressions (10)

### metric_mi 

What metric did they use to assess measurement invariance? (i.e., CFI, RMSEA, other fit measures, you can use abbreviations of fit indices) 

### rule_mi 

What rule did they use for measurement invariance? (i.e., change in CFI < .01, chi-square difference test, etc.). List the rule as what would be considered invariant (i.e., passes the test, groups are considered equal).  

### invariance_claim 

What type of invariance did they claim? Use the step name and their words for the type of invariance. For example, fully invariant to residuals/strict, partially scalar invariant, non-invariant, etc.) 

## ChatGPT Results

### Prompt 

Given the survey questions in Article_Coding_Assessment.docx, answer the survey questions for the panayiotou paper as one answer per row in a tabular format. (attached survey above + pdf)

### Answer 

Here’s a table summarizing the answers for the survey questions based on the Panayiotou et al. paper:

```{r}
pDF <- import("../coding_example/Panayiotou_Survey_Answers.csv")
kable(pDF)
```

This table consolidates relevant information. If you need deeper details on any specific part, let me know!

### Prompt

Do the same thing for the zager paper attached (attached pdf)

### Answer

Here’s a table summarizing the answers for the survey questions based on the Zager Kocjan et al. paper:

-- table included but see note below --

This table consolidates the key survey answers based on the paper. Let me know if you need additional details or refinements!

### Prompt

In the tabular analysis of the Zager paper, reformat the table so that the number of groups, names of groups, and invariance claimed for groups are broken out into separate rows 

### Answer

Here is the reformatted table for the Zager Kocjan et al. paper:

```{r}
zDF <- import("../coding_example/Zager_Survey_Answers.csv")
kable(zDF)
```

This breakout provides separate rows for each group type (countries, genders, ages, and time points) and their respective invariance details. Let me know if you need further refinements!

